---
title: "Calculating and Interpreting A-Values"
author: "Aristotelis Epanomeritakis and Davide Viviano"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calculating and Interpreting A-Values}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Overview

The **avalue** package calculates abstention-values (A-values) for optimal
follow-up experimentation. An A-value is the break-even welfare cost below
which collecting follow-up evidence is preferred to making an immediate
policy decision.

For an initial estimate `X1` with standard error `s1`, define
`w = s2 / s1`, where `s2` is the follow-up standard error. The package
calculates

$$
A(X_1; s_1, w) =
s_1 \inf\{\gamma \ge 0: |X_1|/s_1 \ge \tau^\star(w,\gamma)\}.
$$

Thus, `w = 1` describes an equal-precision follow-up and smaller values
describe a more precise follow-up.

## Basic calculation

Pass a vector of point estimates and either standard errors or exact
two-sided normal p-values. Named estimates are used as estimate IDs.

```{r basic}
library(avalue)

estimates <- c(study_A = 0.20, study_B = -0.10, study_C = 0.55)
standard_errors <- c(0.10, 0.30, 0.20)

result <- calculate_a_values(
  point_estimate = estimates,
  std_error = standard_errors,
  w = 1,
  top_n = 1
)

result$data
```

The returned object has three components:

- `data`: inputs, derived statistics, A-values, ranks, and selections;
- `plots`: three modifiable `ggplot2` objects;
- `settings`: the calculation settings and the definition of `w`.

## Plots

The histogram uses a logarithmic A-value axis. The two scatter plots compare
A-value ranks with p-value ranks and standard-error ranks. Rank 1 means the
largest value under every rule. When `top_n` is supplied, the selected sets
are color coded.

```{r plots, fig.width = 6.5, fig.height = 4.5}
result$plots$histogram
result$plots$p_value_ranks
result$plots$standard_error_ranks
```

The standard plot method displays one or all plots:

```{r plot-method, eval = FALSE}
plot(result, which = "p_value_ranks")
plot(result)
```

## Supplying exact p-values

If standard errors are unavailable, supply exact two-sided normal p-values.
The package recovers each standard error from
`s1 = abs(X1) / qnorm(1 - p / 2)`.

```{r p-values}
from_p <- calculate_a_values(
  point_estimate = c(a = 0.20, b = -0.30),
  p_value = c(0.04550026, 0.23013934)
)

from_p$data[, c("estimate_id", "standard_error", "a_value")]
```

Reported p-values are often rounded. Supply standard errors directly whenever
they are available, because recovering a standard error from a rounded
p-value can distort the A-value.

## Estimate-specific follow-up designs

The precision ratio may be scalar or estimate-specific:

```{r vector-w}
different_designs <- calculate_a_values(
  point_estimate = estimates,
  std_error = standard_errors,
  w = c(1, 0.75, 0.5)
)

different_designs$data[, c("estimate_id", "w", "a_value")]
```


## Ranking and units

A-values have the same welfare units as the point estimates and standard
errors. Convert estimates into comparable welfare units before ranking them
across studies. When a cutoff contains ties, the function breaks ties by
estimate ID so that every rule selects exactly `top_n` estimates.


